Can we explain the popularity of Netflix Shows?

### 2023-01-21 submission.Rmd
save work

@@

# Packages
Before we get started. We will load all the relevant Pacakages
```{r load packages, message=FALSE}
library(reticulate)
library(DBI)
library(dplyr)
library(lubridate)
library(tidyr)
library(data.table)
library(quanteda)
library(tm)
library(lsa)
library("quanteda.textmodels")
library(ggplot2)
library(kableExtra)
```

@@

### Source 1: Kaggle 
This dataset provides us with a list of Netflix Shows along with information such as the year it was added, duration, cast, description etc..
There are altogether 8808 Netflix Shows in this dataset.
```{r}
netflixData <- read.csv(file = 'datasets/dataset_main.csv')
```
```{r echo=FALSE}
# FOR Displaying results
# temp = head(netflixData, 10)
# temp %>%
#   kbl() %>%
#   kable_styling() %>%
#   column_spec(1, width = "10cm") %>%
#   scroll_box(width = "1000px", height = "500px")
```

### Source 2: Google Search Results 
To represent popularity, I will use Google Review Scores, this is also going to be my dependent variable. 
In order to supplement the information from the Kaggle dataset, I extracted other information from Google which will hopefully also serve as independent features.

The image below shows an example of the data that will be collected for each of the 8808 shows in the Kaggle Dataset, namely Review Score, Description, Genre and Language

```{r pressure, echo=FALSE, out.width = '100%'}
knitr::include_graphics("Search Example.JPG")
```

#### Google Scrapping Method
```{python}
def get_source(url):
    try:
        session = HTMLSession()
        response = session.get(url)
        return response
    except requests.exceptions.RequestException as e:
        print(e)

@@

Load Google Search Results dataset.
``` {r}
googleData <- read.csv(file = 'datasets/dataset_googleScraped.csv')
```

@@

# Data Transformation
## Renaming Columns
I rename the columns because some of them had the same names. 
Independent features that were scraped from Google have "google_" at the front of them.
``` {r}
new_names <- c("id" 
        , "type"
        , "title"
        , "director"
        , "cast"
        , "country"
        , "date_added"
        , "release_year"
        , "rating"
        , "duration"
        , "genre"
        , "plot"
        , "google_score"
        , "google_language"
        , "google_genre"
        , "google_plot")
df <- setNames(df, new_names)
```
## Data Preview
Here is what the dataset looks like now, we can see all the features that will be used:
``` {r echo=FALSE}
temp = head(df, 10)
temp %>%
  kbl() %>%
  kable_styling() %>%
  column_spec(1, width = "10cm") %>%
  scroll_box(width = "1000px", height = "500px")
```

## Drop rows
As expected, the Google search results of some Netflix Shows did not give us a Google Review Score.
I drop these rows because there is no point keeping rows with no Dependent Feature.

```{r}
df <- df[grep("%", df$google_score),]
```

# Data Exploration

### Missing Data
```{r}
count_blanks <- function(feature) {
    string1 <- feature
    string2 <- '== ""'
    subset = paste(string1, string2)
    subset <- subset(df, eval(parse(text=subset)))
    count <- count(subset)
  return(count)
}

feature <- new_names # retrieving all the column names

NA_Count <- c(
 toString(count_blanks('id'))
, toString(count_blanks('type'))
, toString(count_blanks('title'))
, toString(count_blanks('director'))
, toString(count_blanks('cast'))
, toString(count_blanks('country'))
, toString(count_blanks('date_added'))
, toString(count_blanks('release_year'))
, toString(count_blanks('rating'))
, toString(count_blanks('duration'))
, toString(count_blanks('genre'))
, toString(count_blanks('plot'))
, toString(count_blanks('google_score'))
, toString(count_blanks('google_language'))
, toString(count_blanks('google_genre'))
, toString(count_blanks('google_plot')))
NA_Count <- data.frame(feature, NA_Count)

print(NA_Count)

@@

@@

Analysing missing datapoints (sub sub header)
< code >
Pretty useless to have these features
But I transform the fields into present/absent
Just in case it has predictive capabilities
< code > 
# See if type needs cleaning

``` {r}
view <- df %>% group_by(type) %>% summarise(count = n()) # Show types and count by each type
print(view)
```

director
``` {r}
view <- df %>% group_by(director) %>% summarise(count = n()) # Show directors and count by each director group
print(view)
```
Some of the rows have more than one director (will make maping tables)

# See if country needs cleaning
``` {r}
view <- df %>% group_by(country) %>% summarise(count = n()) # Show country and count by each country group

```
# Many of the rows have more than one country (will make maping tables)

# See if date_added needs cleaning
``` {r}
view <- df %>% group_by(date_added) %>% summarise(count = n()) # Show date_added and count by each date_added
```
# Change to date format
``` {r}
df$date_added <- mdy(df$date_added)
```
# See if release year needs cleaning
``` {r}
view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
```
# See if rating needs cleaning
``` {r}

view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
df$rating[df$rating == "PG-13" ] <- "PG"
df$rating[df$rating == "TV-PG" ] <- "PG"
df$rating[df$rating == "TV-14" ] <- "PG"
df$rating[df$rating == "TV-G" ] <- "G"
df$rating[df$rating == "TV-MA" ] <- "R"
df$rating[df$rating == "TV-Y7" ] <- "Y"
df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
df$rating[df$rating == "TV-Y" ] <- "Y"
df$rating[df$rating == "NR" ] <- "UR"

```
# See if duration needs cleaning
``` {r}
view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
```
# Duration convert blanks to NA
# Convert duration to numeric

``` {r}
df$duration[df$duration ==""] <- NA
df <- separate(df, duration, c("duration", "duration_units"))
df <- transform(df, duration = as.numeric(duration))
```

# See if genre needs cleaning
``` {r}
view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
```

# See if plot needs cleaning
``` {r}
view <- df %>% group_by(plot) %>% summarise(count = n()) # Show plot and count by each plot
```

# See if google_score needs cleaning
``` {r}
view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
```

# Remove % and convert to numeric type
``` {r}
df$google_score<-gsub("%","",as.character(df$google_score))
df <- transform(df, google_score = as.numeric(google_score))
```

Transform google_language and google_genre feature into present/absent because it was not scrappable
``` {r}
df$google_language <- ifelse(df$google_language =="", "absent", "present")
view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
print(view)
```
``` {r}
df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
view <- df %>% group_by(google_genre) %>% summarise(count = n())
print(view)
```

``` {r}
write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
df <- read.csv(file = 'datasets/view_main_cleaned.csv')
```

>>>>

```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics("netflixHomepage.JPG")
```

@@

# Packages
Before we get started. We will load all the relevant Pacakages
```{r load packages, message=FALSE}
library(reticulate)
library(DBI)
library(dplyr)
library(lubridate)
library(tidyr)
library(data.table)
library(quanteda)
library(tm)
library(lsa)
library("quanteda.textmodels")
library(ggplot2)
library(kableExtra)
library(Hmisc)
```

@@

### Source 1: Kaggle 
This dataset provides us with a list of Netflix Shows along with information such as the year it was added, duration, cast, description etc..
There are altogether 8807 Netflix Shows in this dataset.
```{r}
netflixData <- read.csv(file = 'datasets/dataset_main.csv')
```
```{r echo=FALSE}
# FOR Displaying results
# temp = head(netflixData, 10)
# temp %>%
#   kbl() %>%
#   kable_styling() %>%
#   column_spec(1, width = "10cm") %>%
#   scroll_box(width = "1000px", height = "500px")
```

### Source 2: Google Search Results 
The Kaggle dataset doesn’t contain any feature that gives us information about how popular or likable a show was. 
However, with the Netflix Show title, we can perform some web scraping to obtain Review Scores and other information off Google.

The image below shows an example of the data that will be collected for each of the 8808 shows in the Kaggle Dataset, namely Review Score, Description, Genre and Language
To represent popularity, I will use Google Review Scores, this is also going to be my dependent variable. 
```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics("Search Example.JPG")
```

Google Scrapping Method
Below is the method I use to scrap data off Google. 
```{python}
def get_source(url):
    try:
        session = HTMLSession()
        response = session.get(url)
        return response
    except requests.exceptions.RequestException as e:
        print(e)

@@

Apply data scraping function on all movie/show titles in dataset. 
Once all the information has been scraped, I write it into a csv file (full code in GitHub).
``` {python eval = FALSE}
# data = pd.read_csv('netflix_titles.csv')
# goolgeInfo = data['title'].apply(get_googleInfo)
# goolgeInfo.to_csv('googleInfo.csv', encoding='utf-8', index=False)
print("hi")
```

Since the data scrapping was done in Python, I now need to load all Google Search Results data into the R world of this project.
``` {r}
googleData <- read.csv(file = 'datasets/dataset_googleScraped.csv')
```

@@

Both datasets are now joined but the feature names are quite confusing still. I will rename the features before showing a preview of the full combined dataset I will be working with.

# Previewing Raw Data
## Renaming Columns
I rename the columns because some of them had the same names. 
Independent features that were scraped from Google have "google_" at the front of them.
``` {r}
new_names <- c("id" 
        , "type"
        , "title"
        , "director"
        , "cast"
        , "country"
        , "date_added"
        , "release_year"
        , "rating"
        , "duration"
        , "genre"
        , "plot"
        , "google_score"
        , "google_language"
        , "google_genre"
        , "google_plot")
df <- setNames(df, new_names)
```
## Data Preview
Here is what the dataset looks like now, we can see all the features that will be used:
``` {r echo=FALSE}
temp = head(df, 10)
temp %>%
  kbl() %>%
  kable_styling() %>%
  column_spec(1, width = "10cm") %>%
  scroll_box(width = "1000px", height = "500px")
```

# Cleaning the data

## Removing duplicates or irrelevant observations
## Dealing with duplicates 
Checking if there are any duplicated Netflix Shows
``` {r}
print(length(unique(df$title)))
```

``` {r}
print(df[duplicated(df$title),])
```
The Netflix shows that were thought to be duplicates by the code before seemed like dates instead.
No duplicates. So we can move on.

### Drop rows
Any Netflix Show which does not have a Google Review Score (crucial dependent variable) is an irrelevant observation since it cannot be used for Analysis.
``` {r}
count_blanks <- function(feature) {
    string1 <- feature
    string2 <- '== ""'
    subset = paste(string1, string2)
    subset <- subset(df, eval(parse(text=subset)))
    count <- count(subset)
  return(count)
}

print(count_blanks('google_score'))
```

As expected, the Google search results of some Netflix Shows did not give us a Google Review Score. I drop these rows.
```{r}
df <- df[grep("%", df$google_score),]
```
Below shows and example of a Show which does not give us a Google Review Score
```{r echo=FALSE, out.width = '100%'}
knitr::include_graphics("NoGoogleScore.JPG")
```

We are now left with 6511 rows.
``` {r}
print(length(unique(df$title)))
```

## Fixing structural errors.
Structural errors are when you measure or transfer data and notice strange naming conventions, typos, or incorrect capitalization. These inconsistencies can cause mislabeled categories or classes. For example, you may find “N/A” and “Not Applicable” both appear, but they should be analyzed as the same category. Changing data types

We will look feature by feature for structural errors.

1. Type
``` {r}
view <- df %>% group_by(type) %>% summarise(count = n())
print(view)
```
The type feature looks clean, no action will be taken on it.
Action: None

2. director
``` {r}
view <- df %>% group_by(director) %>% summarise(count = n())
print(view)
```
Some of the rows have more than one director. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

3. Cast
``` {r}
view <- df %>% group_by(cast) %>% summarise(count = n())
print(view)
```
As expected, many Shows have more than one cast member. 
Action: Similar to what will be done with the Director Feature, I will make mapping tables and use feature engineering to capture this variable

3. Country
``` {r}
view <- df %>% group_by(country) %>% summarise(count = n())
print(view)
```
Some shows originated from several different countries.
Action: Similar to what will be done with the Director and Cast Feature, I will make mapping tables and use feature engineering to capture this variable.

4. Date Added
``` {r}
view <- df %>% group_by(date_added) %>% summarise(count = n())
print(view)
print(typeof(df$date_added))
```
Date Added is in the character format.
Action: Change this to date format
``` {r}
df$date_added <- mdy(df$date_added)
```

5. Release Year
``` {r}
view <- df %>% group_by(release_year) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
print(typeof(df$release_year))
```
Release Year has the integer type. No noticable structural error.
Action: None

6. Rating
``` {r}
view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
```
There are several categories which have the same meaning.
Action: Consolidate the categories

Consolidate the categories of the Rating Feature
```{r}
df$rating[df$rating == "PG-13" ] <- "PG"
df$rating[df$rating == "TV-PG" ] <- "PG"
df$rating[df$rating == "TV-14" ] <- "PG"
df$rating[df$rating == "TV-G" ] <- "G"
df$rating[df$rating == "TV-MA" ] <- "R"
df$rating[df$rating == "NC-17" ] <- "R"
df$rating[df$rating == "TV-Y7" ] <- "Y"
df$rating[df$rating == "TV-Y7-FV" ] <- "Y"
df$rating[df$rating == "TV-Y" ] <- "Y"
df$rating[df$rating == "NR" ] <- "UR"
df$rating[df$rating == "66 min" ] <- "UR"
df$rating[df$rating == "84 min" ] <- "UR"

view <- df %>% group_by(rating) %>% summarise(count = n()) # Show release_year and count by each release_year
print(view)
```

7. Duration
``` {r}
view <- df %>% group_by(duration) %>% summarise(count = n()) # Show duration and count by each release_year
print(view)
```
Durations with two different units are in the same feature. Also, we can remove their units to make it integers.
Action: Split column into two different types of durations, remove units
``` {r}
df$duration[df$duration ==""] <- NA
df$duration_min <- ifelse(grepl("min", df$duration),df$duration,NA)
df$duration_season <- ifelse(grepl("Season", df$duration),df$duration,NA)
print(head(df, 10))
```

Remove string from duration and convert character to integer
``` {r}
df$duration_min <-  gsub('min','',df$duration_min)
df$duration_min <- as.numeric(df$duration_min)
df$duration_season <-  gsub('Seasons','',df$duration_season)
df$duration_season <-  gsub('Season','',df$duration_season)
df$duration_season <- as.numeric(df$duration_season)
print(head(df,10))
```

Drop duration column
```{r}
df = subset(df, select = -c(duration))
```

8. Genre
``` {r}
view <- df %>% group_by(genre) %>% summarise(count = n()) # Show genre and count by each genre
print(view)
```
Some of the rows have more than one genre. 
Action: In the next Feature Engineering Section, I will make mapping tables and use feature engineering to capture this variable

9. Plot
Plot contains text data.
Action: Use Latent Semantic Analysis to categorize plots

10. Google Score
``` {r}
view <- df %>% group_by(google_score) %>% summarise(count = n()) # Show google_score and count by each google_score
print(view)
```
Symbol exist and type is character
Action: remove symbol and convert type to numeric

11. Google Score
``` {r}
df$google_score<-gsub("%","",as.character(df$google_score))
df <- transform(df, google_score = as.numeric(google_score))
```

12. Google Language
``` {r}
print(head(df$google_language), 10)
```
Clear that a lot of data is missing.
Action: Extract feature from it (present/absent)

Transform google_language and google_genre feature into present/absent because it was not scrappable
view <- df %>% group_by(google_language) %>% summarise(count = n())  # Show categories and count by each category
df$google_language <- ifelse(df$google_language =="", "absent", "present")
print(view)
df$google_genre <- ifelse(df$google_genre =="", "absent", "present")
view <- df %>% group_by(google_genre) %>% summarise(count = n())
print(view)

13. Google Genre

``` {r}
print(head(df$google_language), 10)
```
Clear that a lot of data is missing.
Action: Extract feature from it (present/absent)

``` {r}
#write.csv(df, "datasets/view_main_cleaned.csv", row.names=FALSE)
#df <- read.csv(file = 'datasets/view_main_cleaned.csv')
```

## Handle Missing data

### Missing Data
``` {r}
#desc <- describe(df)
#print(desc)
```

```{r}
#feature <- new_names # retrieving all the column names

#NA_Count <- c(
#  toString(count_blanks('id'))
# , toString(count_blanks('type'))
# , toString(count_blanks('title'))
# , toString(count_blanks('director'))
# , toString(count_blanks('cast'))
# , toString(count_blanks('country'))
# , toString(count_blanks('date_added'))
# , toString(count_blanks('release_year'))
# , toString(count_blanks('rating'))
# , toString(count_blanks('duration'))
# , toString(count_blanks('genre'))
# , toString(count_blanks('plot'))
# , toString(count_blanks('google_score'))
# , toString(count_blanks('google_language'))
# , toString(count_blanks('google_genre'))
# , toString(count_blanks('google_plot')))
#NA_Count <- data.frame(feature, NA_Count)

#print(NA_Count)

@@

* Validate

* Step 3: Filter unwanted outliers

@@

Analysing missing datapoints (sub sub header)
< code >
Pretty useless to have these features
But I transform the fields into present/absent
Just in case it has predictive capabilities
< code >
